---
title: "Interim Analysis"
author: "Joshua White"
date: "1 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 2)#sets inline code, and all code to only show 2 decimal places.
library(tidyverse)
library(here)
library(car) 
library(ordinal)
library(MASS)
library(brms)
library(skimr)

set.seed(1298)
```

## Load Packages and set seed for reproducibility

```{r load-packages, eval = FALSE}
library(tidyverse)
library(here)
library(car) # for recode function
library(ordinal) # for clmm (cumulative link mixed model) function for frequentist mixed models
library(MASS) # for Polr fucntion(proportional odds logistic regression) when no random effects (clmm doesn't work here)
library(brms)
library(skimr)

set.seed(1298)
```

##Import Data

```{r import-data, warning = FALSE}
d <- read_csv("parsedrawresults1.csv", col_types = "icffffnnfnfc")
d <- d[,2:12]
glimpse(d)
```

##Data Wrangling
####Recode VignetteAnswer variable, create new variable, and reorder data  

```{r data-wrangling}
d$vignetteAnswer[d$answerOrder == "A"] <- recode(d$vignetteAnswer[d$answerOrder == "A"], "1 = 3;
                                                                                          2 = 2;
                                                                                          3 = 1;
                                                                                          4 = 0;
                                                                                          5 = -1;
                                                                                          6 = -2;
                                                                                          7 = -3")

d$vignetteAnswer[d$answerOrder == "B"] <- recode(d$vignetteAnswer[d$answerOrder == "B"], "1 = -3;
                                                                                          2 = -2;
                                                                                          3 = -1;
                                                                                          4 = 0;
                                                                                          5 = 1;
                                                                                          6 = 2;
                                                                                          7 = 3")

###create new variable for vignette type + number -- vignette###
# order levels of factor for easy graphing
order <- c(sprintf("G%d", seq(1:12)), sprintf("L%d", seq(1:12))) 
d$vignette <- paste0(d$vignetteType, d$vignetteNumber) %>% factor(levels = order)

#reorder data frame
d <- d[, c(1:5, 12, 6:11)]
```

## Instruction Checks 

```{r instruction-checks}
# first remove amy's testing data point
amy.testing <- grep("amy", d$postquestion2)
d_amyremoved <- d[-amy.testing,]

#check whether observations fail instruction checks
instr_fail <- d_amyremoved$postquestion1 == "incorrect" | d_amyremoved$dummyVignetteAnswer <= 4

#remove data from main dataset and save for possible later analysis (was a particular question more confusing etc?)
d_removed <- d_amyremoved[instr_fail,]
d_pass <- d_amyremoved[!instr_fail,]

d_removed
```
  
## Quickly Inspect Final Data 

```{r inspect-data}
skim(d_pass)
```

## Graph responses

```{r graph}
#make plot
ggplot(d_pass, aes(x = vignette, y = vignetteAnswer, fill = vignetteType)) + 
  geom_jitter(width = 0.15, height = 0.15) +
  stat_summary(fun.y=mean, geom="bar") +
  ylim(c(-3.5, 3.5))

```

## Data analysis: Fit ordinal logistic regression models

First, make vignetteAnswer an ordered factor
```{r order-vignetteAnswer}
d_pass$vignetteAnswer<- ordered(d_pass$vignetteAnswer, levels = c("-3", "-2", "-1", "0", "1", "2", "3"))

```

###Frequentist

```{r frequentist-analysis}
olm.freq.nopred <-  polr(vignetteAnswer ~ 1, data = d_pass, method = "logistic", Hess = TRUE) 
olm.freq.GLpred <-  polr(vignetteAnswer ~ vignetteType, data = d_pass, method = "logistic", Hess = TRUE) 
olm.freq.ordpred <- polr(vignetteAnswer ~ answerOrder, data = d_pass, method = "logistic", Hess = TRUE) 
olmm.freq <-  clmm(vignetteAnswer ~ vignetteType + (1|vignette), data = d_pass, link = "logit", nAGQ = 10) #values between 5 and 10 generally provide accurate maximum likelihood estimates -- documentation

summary(olm.freq.nopred)
summary(olm.freq.GLpred)
summary(olm.freq.ordpred)
summary(olmm.freq)
```

####AIC values
The AIC values for our four different frequentist models are:

* `r AIC(olm.freq.nopred)` for the model with no predictors 
* `r AIC(olm.freq.GLpred)` for the model with Gain or Loss as a predictor
* `r AIC(olm.freq.ordpred)` for the model with answer order as a predictor
* `r AIC(olmm.freq)` for the mixed model with Gain or Loss and a random effect for vignette as predictors

Therefore, the most effective model is the mixed model, showing that there particpant ambiguity aversion is predicted both by whether the vignette was about a gain or a loss, and a random effect for vignette. The model taking into account answer order as a predictor had the worst Akaike Information Criterion, providing evidence that answer order did not effect participant responses. 

### Bayesian

```{r bayesian-analysis, warning = FALSE}
olm.bayes.nopred <-  brm(vignetteAnswer ~ 1, data = d_pass, family = cumulative(link = "logit"), 
                         refresh = 0, open_progress = FALSE)  #to suppress progress printing to screen for .Rmd
olm.bayes.GLpred <-  brm(vignetteAnswer ~ vignetteType, data = d_pass, family = cumulative(link = "logit"), 
                         refresh = 0, open_progress = FALSE) 
olm.bayes.ordpred <- brm(vignetteAnswer ~ answerOrder, data = d_pass, family = cumulative(link = "logit"), 
                         refresh = 0, open_progress = FALSE) 
olmm.bayes <- brm(vignetteAnswer ~ vignetteType + (1|vignette), data = d_pass, family = cumulative(link = "logit"), 
                  refresh = 0, open_progress = FALSE) 

summary(olm.bayes.nopred)
summary(olm.bayes.GLpred)
summary(olm.bayes.ordpred)
summary(olmm.bayes)
```

####WAIC values
The WAIC values for our four different Bayesian models are (I was not able to easily extract the AIC from these models):

* `r WAIC(olm.bayes.nopred)$estimates[3,1]` for the model with no predictors 
* `r WAIC(olm.bayes.GLpred)$estimates[3,1]` for the model with Gain or Loss as a predictor
* `r WAIC(olm.bayes.ordpred)$estimates[3,1]` for the model with answer order as a predictor
* `r WAIC(olmm.bayes)$estimates[3,1]` for the mixed model with Gain or Loss and a random effect for vignette as predictors

Therefore, the most effective model is the mixed model, showing that there particpant ambiguity aversion is predicted both by whether the vignette was about a gain or a loss, and a random effect for vignette. The model taking into account answer order as a predictor had the worst WAIC, providing evidence that answer order did not effect participant responses.