---
title: "Experiment 3 Timepoint 1 Analysis"
author: "Josh White"
date: "03/01/2022"
output: 
  html_document:
    df_print: paged
    theme: journal
    code_folding: hide
    toc: true
    toc_depth: 4
    toc_float:
        collapsed: false
        smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, cache = TRUE, message = FALSE)

library(tidyverse)
library(here)

# Visualisation
library(ggsci)
library(ggrepel)
library(moderndive) # for geom_parallel_slopes_function because there is no way to do this in 

# Modeling
library(lme4)
library(ordinal) # for clmm function
library(brms) # for Bayesian analyses

# Tables
library(flextable)
library(ftExtra)

theme_set(theme_classic())

set.seed(3838)
```

# Introductory Steps

## Load Packages and set seed for reproducibility

```{r load-packages, eval = FALSE}
library(tidyverse)
library(here)

# Visualisation
library(ggsci)
library(ggrepel)
library(moderndive) # for geom_parallel_slopes_function because there is no way to do this in 

# Modeling
library(lme4)
library(ordinal) # for clmm function
library(brms) # for Bayesian analyses

# Tables
library(flextable)
library(ftExtra)

theme_set(theme_classic())

set.seed(3838)
```

## Import Data

```{r import-data, warning = FALSE}
d <- read_csv(
  here::here("experiment3", "timepoint1", "data", "exp3a-data.csv"),
  na = c("", "NA", "na")
  )

#make factors 
d <- d %>% 
  mutate(
    gender = factor(gender),
    income = factor(income, levels = c("<20k", "20to40k", "40to60K", "60to80k", "80to100k", ">100k")), 
    vignette = factor(vignette, levels = c("G1", "G2", "G5", "G9", "G11", 
                                           "L1", "L2", "L5", "L10", "L11"))
  )

#get prior and other variables needed for models
d <- d %>%  
  mutate(
    prior = case_when(
      grepl("G", vignette) ~ xprob - yprob,
      grepl("L", vignette) ~ yprob - xprob
    ),
    direction = case_when(
      grepl("G", vignette) ~ "G",
      grepl("L", vignette) ~ "L"
    )
  )

#get whether passed attn_check or not
d <- d %>% 
  mutate(
    attn_pass = dummyxprob > 50
  )

# get basic descriptives before exclusion
demo_d <- d %>% 
  distinct(subject, gender, age, education, income, attn_pass)

demo_d %>%  skimr::skim()

demo_d %>% 
  count(gender) %>% 
  arrange(desc(n)) %>% 
  flextable::flextable()

demo_d %>% 
  ggplot(aes(x = age)) + 
  geom_histogram(fill = "light blue", col = "black") +
  annotate(geom = "text", x = 60, y = 25,
            label = paste0("M (SD) = ", round(mean(demo_d$age), 2), " (", round(sd(demo_d$age), 2), ")")
  )


demo_d %>% 
  ggplot(aes(x = education)) + 
  geom_histogram(fill = "light blue", col = "black") +
  annotate(geom = "text", x = 25, y = 50,
            label = paste0("M (SD) = ", round(mean(demo_d$education, na.rm = TRUE), 2), 
                           " (", round(sd(demo_d$education, na.rm = TRUE), 2), ")")
  )


demo_d %>% 
  count(income) %>% 
  arrange(desc(n)) %>% 
  flextable::flextable()

```

### exclude participants

```{r exclude}
#check whether observations fail instruction checks
demo_d %>% 
  count(attn_pass) %>% 
  flextable::flextable()

#get list of participants that failed attention check 
subjID_pass <- demo_d$subject[demo_d$attn_pass]
subjID_fail <- demo_d$subject[!demo_d$attn_pass]

# write both to csv
write.csv(subjID_pass, "subjID_pass.csv")
write.csv(subjID_fail, "subjID_fail.csv")

d_pass <- d[d$attn_pass, ]

```

### descriptives

```{r datawrangle, fig.height=7, fig.width = 5}
library(ggdist)

d_pass %>% 
  ggplot(aes(x = prior)) +
  geom_density() +
  facet_wrap(~vignette)

# using ggdists
d_pass %>% 
  ggplot(aes(x = prior, y = fct_rev(vignette), fill = vignette)) +
  stat_halfeye(point_interval = "mean_hdci",
               .width = c(.66, .95),
               slab_alpha = 0.5,
               normalize = "groups", 
               show.legend = FALSE) +
  ggsci::scale_fill_d3() +
  labs(y = "vignette",
       caption = paste(sep = "\n", 
                       "'prior' coded as P(favourable event) - P(unfavourable event).",
                       "positive values indicate optimistic prior beliefs", 
                       "negative values indicate pessimistic prior beliefs")
       )

  # scatter and means
d_pass %>% 
  ggplot(aes(x = vignette, y = prior, fill = direction)) +
  geom_jitter(alpha = 0.25) +
  stat_summary(geom = "bar", fun = mean, alpha = 0.75) +
  stat_summary(geom = "errorbar", fun.data = mean_se, alpha = 0.75, width = 0.5) 


## confidence ratings
d_pass %>% 
  ggplot(aes(x = vignette, y = conf, fill = direction)) +
  geom_jitter(alpha = 0.1) +
  stat_summary(fun = mean, geom = "point", alpha = 1, col = "black", shape = 22, size = 2) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.25, size = 0.5, linetype = 1, show.legend = FALSE) +
  xlab("Vignette") +
  ylab("Confidence rating") +
  scale_y_continuous(breaks = 0:4, labels = c("None", "Slight", "Moderate", "Very", "Extreme")) +
  scale_fill_manual(values = c("dodgerblue", "red2"))


```


## Order effects here

There is evidence of some order effects here. In both Bayesian and Frequentist manifestations, the IC is lower for the model including `trialn` parameter than the null model. This effect is quite small, and equates to a 4.3 point increase in `prior` for the last trial compared to the first trial. 

```{r,  class.source = "fold-show"}
library(lme4)

m0 <- lmer(prior ~ 1 + (1|subject) + (1|vignette), d_pass)
m_order <- lmer(prior ~ 1 + trialn + (1|subject) + (1|vignette), d_pass)

AIC(m0)
AIC(m_order)

summary(m0)
summary(m_order)

#bayes
m0_bayes <- brm(prior ~ 1 + (1|subject) + (1|vignette), 
                data = d_pass,
                cores = 4,
                refresh = 0, open_progress = FALSE)

m_order_bayes <- brm(prior ~ 1 + trialn + (1|subject) + (1|vignette), 
                     data = d_pass, 
                     cores = 4,
                     refresh = 0, open_progress = FALSE)

#MODELS
m0_bayes %>%  summary()
m_order_bayes %>%  summary()

##LOO COMPARE
loo(m0_bayes)
loo(m_order_bayes)

## Plot to see  -- effect is very small
d_pass %>% 
  ggplot(aes(x = trialn, y = prior)) +
  geom_jitter() +
  geom_smooth(method = "lm")

## distribution at each timepoint 

d_pass %>% 
  ggplot(aes(x = trialn, fill = vignette)) +
  geom_bar() +
  ggsci::scale_fill_d3()

#our pattern of only accepting the pair vignette that was three apart, selected a distribution in which 
# the non-pairs were more likely in the middle of the order, while the paris were more likely at the end. 

# no clear or consistent relationship among vignettes. 
d_pass %>% 
  ggplot(aes(x = trialn, y = prior)) +
  geom_jitter() +
  geom_smooth(method = "lm") +
  facet_wrap(~vignette)


```

```{r, fig.width = 7, fig.height= 10}

#pattern not obvious at the individual level
d_pass %>% 
  ggplot(aes(x = trialn, y = prior)) +
  geom_line() +
  facet_wrap(~subject, ncol = 11) +
  scale_x_continuous(breaks = c(2, 5, 8)) +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    #axis.text.x = element_text(angle = 45, hjust = 1)
  )

```

## Relative order effects

Relative order has small effect on responses. When the gain response is shown first there is on average a 3.5 point more favourable `prior` rating higher when gain vignette is shown first than when loss is shown first.  

```{r, class.source = "fold-show"}
d_pairs <- d_pass %>% 
  filter(vignette %in% c("G1", "L1", "G2", "L2", "G5", "L5"))

d_pairs <- d_pairs %>% 
  mutate(
    pair = case_when(
      vignette %in% c("G1", "L1") ~ "ones",
      vignette %in% c("G2", "L2") ~ "twos",    
      vignette %in% c("G5", "L5") ~ "fives",    
    )
)

#code rel_order variable, which is TRUE when gain version of pair occurs first and FALSE when Loss version is
d_pairs <- d_pairs %>% 
  group_by(pair, subject) %>% 
  mutate(
    rel_order_gfirst = trialn[grepl("G", vignette)] < trialn[grepl("L", vignette)]
  ) %>% 
  ungroup()

## MODEL
#freq
m0_pairs <- lmer(prior ~ 1 + (1|subject) + (1|vignette), d_pairs)
m_relorder <- lmer(prior ~ 1 + rel_order_gfirst + (1|subject) + (1|vignette), d_pairs)

AIC(m0_pairs)
AIC(m_relorder)

summary(m0_pairs)
summary(m_relorder)


#bayes
m0_pairs_bayes <- brm(prior ~ 1 + (1|subject) + (1|vignette), 
                data = d_pairs,
                cores = 4,
                refresh = 0, open_progress = FALSE)

m_relorder_bayes <- brm(prior ~ 1 + rel_order_gfirst + (1|subject) + (1|vignette), 
                        #refresh = 0, open_progress = FALSE,
                        data = d_pairs, 
                        cores = 4)

#MODELS
m0_pairs_bayes %>%  summary()
m_relorder_bayes %>%  summary()

##LOO COMPARE
loo(m0_pairs_bayes)
loo(m_relorder_bayes)


## plot
##pattern doesn't appear to be obvious. but overall, higher when gain is first than when gain is second. 
d_pairs %>% 
  ggplot(aes(x = vignette, y = prior, fill = rel_order_gfirst)) +
  stat_summary(geom = "bar", fun = "mean", position = "dodge") +
  geom_jitter()
  
```